Towards a Pandemic-Scale Ancestral Recombination Graph of SARS-CoV-2

### 2023-04-11 paper.tex
Add cophylogeny fig

Figure 4 shows a co-phylogeny of the 88 samples shared between the wide ARG and
a GISAID global "all-time" tree from NextStrain (downloaded on January 21,
2023). To reduce the ARG to a single tree, we show the very first tree in the
wide ARG; however, the five other trees in this simplified ARG show
near-identical patterns. Supplementary Figure 3 shows the same comparison for
the long ARG. It is clear that the backbone topology of the sc2ts tree shows
very close agreement with the NextStrain tree. The sample genomes cluster by
their assigned Pango lineage status, and many variants and their descendents
form identical monophyletic clades in both the trees (e.g., the Alpha and Delta
clades).

>>>>

\begin{figure} \centering
\includegraphics[width=\textwidth]{figures/cophylogeny_wide.pdf}
\caption{\label{fig:cophlogeny} DESCRIBE ME.
}
\end{figure}

Figure~\ref{fig:cophlogeny} shows a co-phylogeny of the 88 samples shared between the wide ARG and
a GISAID global "all-time" tree from NextStrain (downloaded on January 21,
2023). To reduce the ARG to a single tree, we show the very first tree in the
wide ARG; however, the five other trees in this simplified ARG show
near-identical patterns. Supplementary Figure 3 shows the same comparison for
the long ARG. It is clear that the backbone topology of the sc2ts tree shows
very close agreement with the NextStrain tree. The sample genomes cluster by
their assigned Pango lineage status, and many variants and their descendents
form identical monophyletic clades in both the trees (e.g., the Alpha and Delta
clades).
